%====================
% Intent Letter
%====================

% \hfill \break

March 6, 2024\\

\vspace{2.0ex}

The Ohio State University \\
Fisher College of Business  \\
Department of Operations and Business Analytics \\
2100 Neil Avenue \\
Columbus, Ohio 43210 \\

\vspace{2.0ex}

Dear Members of the Search Committee, \\

\vspace{2.0ex}

% JSL version 10/17/23 is below

I am writing to apply for the position of Senior Lecturer in the Department of  Operations and Business Analytics, as announced on your department website.  I am highly interested in obtaining a position at such a prestigious department that prepares students to become leaders in the global economy.  I strongly believe that my successful track record in the corporate world, which spans more than two decades, coupled with my academic, research and teaching background, aligns well with the department's objectives of producing future problem solvers and changemakers who will make an impact in the business world and beyond. \\

\vspace{2.0ex}

My professional experience in operations management, data analysis, and business analytics includes many development and deployment projects where the principles of six sigma and total quality management were applied.  I developed proprietary product assortment algorithms that are used to reduce the number of SKUs in a retailer's assortment while minimizing revenue and profitability risks.  I also developed a shelf-space optimization algorithm that is used to determine shelf-space allocations and slotting allowances;  these solutions are  currently being used by companies in the global beauty, hard-line retailing, and soft-line retailing verticals.  Additionally, I led a team that developed a novel item-level pricing model specification and optimization algorithm that determines the items to be offered on a menu and their price by location;  the solution is deployed for quick-serve restaurants and family causal dining restaurants.  

\vspace{2.0ex}

I have also used my background in analytics, statistics, and econometrics to measure the effectiveness of marketing. I have successfully designed, executed and analyzed randomized control trial experiments and surveys; for those applications where only observational study data is available, I have used methods that mitigate the consequences of potential endogeneity, such as marketing mix modeling using instrumental variable approaches, double machine learning, and targeted maximum likelihood estimation.  I have also designed and implemented automated and scalable unsupervised statistical methods that are used to conduct customer segmentation, and advanced supervised statistical methods such as random forests and deep learning, to predict customers who are expected either to be the most responsive, or most incremental, for a marketing tactic exposure.  The focus of my current consulting engagements is on the quality, accuracy and precision of cross-media measurement metrics for data of varying sizes and selection mechanisms.% and using Google Marketing Platform products to inform advertising decision-making.\\

\newpage

From a strategic business perspective the principles of six sigma DMAIC (define, measure, analyze, improve and control) methodology were used by me and the team I managed to vet the quality, completeness, and stability of Quotient Technology frequent shopper card data;   this data is used in production systems that measure the effectiveness of advertising and promotions. We also applied the ideas to digital activity signals, typically email address-device pair combinations, from Truedata, Neustar, Throtle, and other digital data providers, to determine the appropriateness of including their data into the Nielsen Identity Graph; the Nielsen Identify Graph is used to join advertising impressions across devices, platforms and media.  

\vspace{2.0ex}

During my professional career I was frequently appointed to apply my knowledge of operations and analytics to determine the viability of a strategic business initiative.  As a case in point I conducted multi-quarter data analytic and algorithm due diligence of several start-ups;  this work led to the Nielsen acquisition of VisualIQ in 2017 and TVTY in 2021, and the decision to not acquire several other potential start-ups.  Furthermore, I was an integral member of the Nielsen data science team that was responsible for preparting and presenting Nielsen data processing and data science methods with a private equity consortium led by Elliott Investment Management and Brookfield Business Partners;  in 2022 the consortium acquired Nielsen for \$16B. 

\vspace{2.0ex}

My objective as an instructor is to motivate my students to develop their own learning interests and critical thinking skills while working in a collaborative and open environment.  When teaching analytics classes, my discussions are primarily centered on empirical business applications.  For analytic business projects, students are encouraged to discuss challenges and exchange ideas.  Through many years of producing successful business results and leading and mentoring more than fifty associates, I have discovered that success is achieved through leaders who are approachable, promote a creative work environment, offer constructive feedback and acknowledge success.  I have discovered that applying these same principles in the classroom have yielded equally positive results.  \\

\vspace{2.0ex}

I am enthusiastic about discussing this position with you in the weeks to come. In the meantime, I am enclosing my curriculum vitae.  If you require any additional materials or information, I am happy to supply them. Thank you very much for your consideration. \\

% BKW version 10/14/23 is below

\begin{comment}

\vspace{2.0ex}

I am writing to apply for the position of Senior Lecturer in the Department of Marketing and Logistics, as advertised on your department website.  I am highly interested in obtaining a position at such a prestigious department, where I can contribute to preparing students to become leaders in global corporations.  I believe that my corporate marketing analytic research and development efforts, which spans more than two decades in the industry, is closely aligned with the department's instructional goals of providing high-quality, real-world applications and case studies. \\

\vspace{2.0ex}

To measure the effectiveness of marketing I have successfully designed, executed and analyzed randomized control trial experiments and surveys.  For those applications where only observational study data is available, I have used methods that mitigate the consequences of potential endogeneity, such as marketing mix modeling using instrumental variable approaches, double machine learning, and targeted maximum likelihood estimation.  Additionally, I have designed and implemented automated and scalable unsupervised statistical methods that are used to conduct customer segmentation, and advanced supervised statistical methods, such as random forests and deep learning, to predict customers who are expected either to be the most responsive, or most incremental, for a marketing tactic exposure.  The focus of my current consulting engagements is on the quality, accuracy and precision of cross-media measurement metrics for data of varying size and selection mechanisms. \\

\vspace{2.0ex}

My objective as an instructor is to motivate my students to develop their own learning interests and critical thinking skills while working in a collaborative and open environment.  When teaching analytics classes my discussions are always centered empirical business applications.  For analytic business projects students are encouraged to discuss challenges and exchange ideas.  Based in part on that part of my professional career where I managed organizations that exceeded scores of associates, I discovered that leadership is fostered by being approachable, creating a positive work environment, offering constructive feedback, and acknowledging success.  I believe these guiding principles have served students well in the classroom also. \\

\vspace{2.0ex}

I would enjoy discussing this position with you in the weeks to come. In the meantime, I am enclosing my curriculum vitae and list of courses taught.  If you require any additional materials or information, I am happy to supply it. Thank you very much for your consideration. \\

\end{comment}

\vspace{4.0ex}

Sincerely, \\
\vspace{2.0ex}
Brian Weikel.
